Scale Space Edge Detection

### 2018-03-09 paper.tex
Add rough draft of marching cubes algorithm

%&pdflatex
\documentclass{article}
\usepackage[final]{nips_2017}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{tabu}
\usepackage{morefloats}
\usepackage{float}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{commath}
\usepackage{graphicx}

@@

\section*{Appendix}

>>>>

%&pdflatex
\documentclass{article}
\usepackage[final]{nips_2017}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{tabu}
\usepackage{mathrsfs}
\usepackage{morefloats}
\usepackage{float}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{commath}
\usepackage{graphicx}
\usepackage{tikz,tikz-3dplot}
\usetikzlibrary{calc}
\usetikzlibrary{intersections}

@@

\subsection{Marching Cubes}

We note that the equations $\partial_t (\mathcal G_{\text{$\gamma$-norm}} L) =0 $ and $L_{vv} = 0$ define isosurfaces $\mathcal Z_1$ and $\mathcal Z_2$, embedded in $L$.
Computing the intersection of these two surfaces and requiring the local maxima conditions $\partial_{tt} (\mathcal G_{\text{$\gamma$-norm}} L) < 0$ and $L_{vvv} < 0$ yields a family of isocurves, also embedded in $L$, which directly correspond to the edges in the image.

However, since we only have access to $\partial_t (\mathcal G_{\text{$\gamma$-norm}} L)$ and $L_{vv}$ at the lattice points of $L$, we cannot solve for their intersection analytically.
Instead, we rely on an approximation method to find the edges.
We have chosen to implement the algorithm sketched by Lindeberg, a variation of the marching cubes algorithm.

In our implementation, $L$ is broken down into voxels with a value at every corner.
\begin{lstlisting}
function marching_cubes(x, y, t, visited)
    if visited[x, y, t]
        return Set()
    end

    visited[x, y, t] = true
\end{lstlisting}
Since edges are connected sets of points, we know that if a given voxel has already been visited it cannot be part of this edge, so we skip it.

\begin{lstlisting}
    const corners = (x:x+1, y:y+1, t:t+1)

    # Note: Maybe they don't need to be in the same corner
    if !(any(view(GLtt, corners...)) && any(view(Lvvv, corners...)))
      return Set()
    end
\end{lstlisting}
We then check that our sign conditions $\mathcal S_1 < 0$ and $\mathcal S_2 < 0$ are each negative in at least one vertex of the voxel, otherwise there can be no maxima of $\mathcal Z_1$ and $\mathcal Z_2$ inside this voxel.
\begin{lstlisting}
    @views Z1, Z2 = Lvv[corners...], GLt[corners...]
    Z1_crossings = Array{Tuple{NTuple{3,Int}, NTuple{3,Int}, Array{Float64, 1}}, 1}()
    Z2_crossings = Array{Tuple{NTuple{3,Int}, NTuple{3,Int}, Array{Float64, 1}}, 1}()

    # Find all sign crossings w/ linear interpolation
    for (a, b) in cube_edges
        if signbit(Z1[a...]) != signbit(Z1[b...])
            push!(Z1_crossings, (a, b, linear_interpolate(a, b, Z1[a...], Z1[b...])))
        end

        if signbit(Z2[a...]) != signbit(Z2[b...])
            push!(Z2_crossings, (a, b, linear_interpolate(a, b, Z2[a...], Z2[b...])))
        end
    end
\end{lstlisting}

We then construct a list of edges where the signs of $\mathcal Z_1$ or $\mathcal Z_2$ differ at the endpoints of the edge.
We then estimate the position of the zero crossing of the surface of that point using linear interpolation.
\begin{lstlisting}
    for (normal, face) in cube_faces
        Z1_zeros, Z2_zeros = [], []
        for (a, b, mid) in Z1_crossings
            if a in face && b in face
                push!(Z1_zeros, mid)
            end
        end

        for (a, b, mid) in Z2_crossings
            if a in face && b in face
                push!(Z2_zeros, mid)
            end
        end
\end{lstlisting}
Then, for every face of the voxel, we collect all of the edges with a zero crossing that lie on that face.
\begin{lstlisting}
        # Reject if there are more than two crossings for either invariant
        if !(length(Z1_zeros) == length(Z2_zeros) == 2)
            continue
        end
\end{lstlisting}
If there is only one edge with a zero crossing on that face, the face cannot have a zero crossing inside it, so we skip further processing on this face.
If there are four zero crossings of either invariant on this face, then it is ambiguous how the isosurface intersects with the face, so we will skip it\footnote{In the future, we could try to resolve this situation, since there are only two possible cases.} Here is a visualization of one case satisfying these requirements:

\tdplotsetmaincoords{70}{120}
\begin{center}
  \begin{tabu}{cc}
    \toprule
    $\mathcal Z_1 $(i.e. $L_{vv}$)& $\mathcal Z_2$ (i.e. $\mathcal{G}L_t$)\\
    \midrule
    \begin{tikzpicture}[scale=0.5,tdplot_main_coords]
      % The vertex at V
      \tdplotsetcoord{P}{sqrt(3)*5}{55}{45}
      \tdplotsetcoord{O}{0}{0}{0}

      \draw[]
      (0,0,0) -- (Px)
      (0,0,0) -- (Py)
      (0,0,0) -- (Pz);

      \draw[] (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
      \draw[] (Pyz) -- (Py) -- (Pxy);

      \node[fill,circle,inner sep=1.75pt] at ($ (P)!0.63!(Pyz) $) {};
      \node[fill,circle,inner sep=1.75pt] at ($ (Pxy)!0.45!(Py) $) {};
      \draw [thick] ($ (P)!0.63!(Pyz) $)--($ (Pxy)!0.45!(Py) $);

      \node[fill,circle,inner sep=1.75pt] at ($ (Pxz)!0.4!(Pz) $) {};
      \node[fill,circle,inner sep=1.75pt] at ($ (Px)!0.75!(O) $) {};
      \draw [thick] ($ (Pxz)!0.4!(Pz) $)--($ (Px)!0.75!(O) $);

      \node[label=above:$+$,fill,circle,inner sep=1.3pt] at (P) {};
      \node[label=below left:$+$,fill,circle,inner sep=1.3pt] at (Px) {};
      \node[label=below right:$-$,fill,circle,inner sep=1.3pt] at (Py) {};
      \node[label=above:$-$,fill,circle,inner sep=1.3pt] at (Pz) {};
      \node[label=below:$+$,fill,circle,inner sep=1.3pt] at (Pxy) {};
      \node[label=above right:$-$,fill,circle,inner sep=1.3pt] at (Pyz) {};
      \node[label=above left:$+$,fill,circle,inner sep=1.3pt] at (Pxz) {};
      \node[label=above right:$-$,fill,circle,inner sep=1.3pt] at (O) {};
    \end{tikzpicture} &
    \begin{tikzpicture}[scale=0.5,tdplot_main_coords]
      % The vertex at V
      \tdplotsetcoord{P}{sqrt(3)*5}{55}{45}
      \tdplotsetcoord{O}{0}{0}{0}

      \draw[]
      (0,0,0) -- (Px)
      (0,0,0) -- (Py)
      (0,0,0) -- (Pz);

      \draw[]
      (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
      \draw[]
      (Pyz) -- (Py) -- (Pxy);

      \node[fill,circle,inner sep=1.75pt] at ($ (Px)!0.63!(Pxz) $) {};
      \node[fill,circle,inner sep=1.75pt] at ($ (O)!0.3!(Pz) $) {};
      \draw [thick] ($ (Px)!0.63!(Pxz) $)--($ (O)!0.3!(Pz) $);

      \node[fill,circle,inner sep=1.75pt] at ($ (Pxy)!0.7!(P) $) {};
      \node[fill,circle,inner sep=1.75pt] at ($ (Py)!0.3!(Pyz) $) {};

      \draw [thick] ($ (Pxy)!0.7!(P) $)--($ (Py)!0.3!(Pyz) $);

      \node[label=above:$+$,fill,circle,inner sep=1.3pt] at (P) {};
      \node[label=below left:$-$,fill,circle,inner sep=1.3pt] at (Px) {};
      \node[label=below right:$-$,fill,circle,inner sep=1.3pt] at (Py) {};
      \node[label=above:$+$,fill,circle,inner sep=1.3pt] at (Pz) {};
      \node[label=below:$-$,fill,circle,inner sep=1.3pt] at (Pxy) {};
      \node[label=above right:$+$,fill,circle,inner sep=1.3pt] at (Pyz) {};
      \node[label=above left:$+$,fill,circle,inner sep=1.3pt] at (Pxz) {};
      \node[label=above right:$-$,fill,circle,inner sep=1.3pt] at (O) {};
    \end{tikzpicture}\\
    \bottomrule
  \end{tabu}
\end{center}
We then continue our processing:
\begin{lstlisting}
        # Check that the intersection lies on a face
        distance, midpoint = get(intersect)
        if distance > epsilon || !all(1 - epsilon .<= midpoint .<= 2 + epsilon)
            continue
        end

        push!(face_intersections, normal)
\end{lstlisting}
We check whether or not the lines caused by connecting the estimated zero crossings of the edges on the face intersect.
If they do, we mark that face as featuring an intersection, as shown here:
\begin{center}
  \begin{tikzpicture}[scale=0.5,tdplot_main_coords]
    % The vertex at V
    \tdplotsetcoord{P}{sqrt(3)*5}{55}{45}
    \tdplotsetcoord{O}{0}{0}{0}

    \draw[]
    (0,0,0) -- (Px)
    (0,0,0) -- (Py)
    (0,0,0) -- (Pz);

    \draw[]
    (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
    \draw[]
    (Pyz) -- (Py) -- (Pxy);

    \draw[fill,fill opacity=0.15] (P) -- (Pyz) -- (Py) -- (Pxy);
    \draw[fill,fill opacity=0.15] (O) -- (Pz) -- (Pxz) -- (Px);

    \draw [thick, name path=face1a] ($ (Px)!0.63!(Pxz) $)--($ (O)!0.3!(Pz) $);
    \draw [thick, name path=face1b] ($ (Pxz)!0.4!(Pz) $)--($ (Px)!0.75!(O) $);

    \draw [thick, name path=face2a] ($ (Pxy)!0.7!(P) $)--($ (Py)!0.3!(Pyz) $);
    \draw [thick, name path=face2b] ($ (P)!0.63!(Pyz) $)--($ (Pxy)!0.45!(Py) $);

    \path [name intersections={of=face1a and face1b,by=F1}];
    \path [name intersections={of=face2a and face2b,by=F2}];

    \node[fill,circle,inner sep=1.7pt] at (F1) {};
    \node[fill,circle,inner sep=1.7pt] at (F2) {};
  \end{tikzpicture}
\end{center}
Continuing our processing:
\begin{lstlisting}
    if length(face_intersections) == 2
        for normal in face_intersections
            next_voxel = [x, y, t] + normal
            if all(1 .<= next_voxel .<= size(visited))
                union!(result, marching_cubes(next_voxel..., visited))
            end
        end
        push!(result, (x, y, t))
    end
\end{lstlisting}
If there are exactly two faces with zero crossings, then the voxel contains an edge segment.
We then extend the line defined by connecting the estimated intersection points on each face into the neighboring voxels:
\begin{center}
  \begin{tikzpicture}[scale=0.5,tdplot_main_coords]
    % The vertex at V
    \tdplotsetcoord{P}{sqrt(3)*5}{55}{45}
    \tdplotsetcoord{O}{0}{0}{0}

    \draw[]
    (0,0,0) -- (Px)
    (0,0,0) -- (Py)
    (0,0,0) -- (Pz);

    \draw[]
    (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
    \draw[]
    (Pyz) -- (Py) -- (Pxy);

    \draw[transform canvas={shift={(Py)}}]
    (0,0,0) -- (Px)
    (0,0,0) -- (Py)
    (0,0,0) -- (Pz);
    \draw[transform canvas={shift={(Py)}}]
    (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
    \draw[transform canvas={shift={(Py)}}]
    (Pyz) -- (Py) -- (Pxy);

    \draw[transform canvas={shift={($(0,0,0) - (Py)$)}}]
    (0,0,0) -- (Px)
    (0,0,0) -- (Py)
    (0,0,0) -- (Pz);
    \draw[transform canvas={shift={($(0,0,0) - (Py)$)}}]
    (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
    \draw[transform canvas={shift={($(0,0,0) - (Py)$)}}]
    (Pyz) -- (Py) -- (Pxy);

    \draw[fill,fill opacity=0.15] (P) -- (Pyz) -- (Py) -- (Pxy);
    \draw[fill,fill opacity=0.15] (O) -- (Pz) -- (Pxz) -- (Px);

    \draw [dashed, name path=face1a] ($ (Px)!0.63!(Pxz) $)--($ (O)!0.3!(Pz) $);
    \draw [dashed, name path=face1b] ($ (Pxz)!0.4!(Pz) $)--($ (Px)!0.75!(O) $);

    \draw [dashed, name path=face2a] ($ (Pxy)!0.7!(P) $)--($ (Py)!0.3!(Pyz) $);
    \draw [dashed, name path=face2b] ($ (P)!0.63!(Pyz) $)--($ (Pxy)!0.45!(Py) $);

    \path [name intersections={of=face1a and face1b,by=F1}];
    \path [name intersections={of=face2a and face2b,by=F2}];

    \draw [thick, <->] ($(F1)!-0.5!(F2)$) -- ($(F1)!1.5!(F2)$);

    \node[fill,circle,inner sep=1.7pt] at (F1) {};
    \node[fill,circle,inner sep=1.7pt] at (F2) {};

  \end{tikzpicture}
\end{center}
The process is then repeated on the neighboring voxels until we have traversed the entire edge connected to this point.

% \begin{tikzpicture}[tdplot_main_coords]
%   % The vertex at V
%   \tdplotsetcoord{P}{sqrt(3)*5}{55}{45}
%   \tdplotsetcoord{O}{0}{0}{0}

%   \draw[thick]
%   (0,0,0) -- (Px)
%   (0,0,0) -- (Py)
%   (0,0,0) -- (Pz);

%   \draw[thick]
%   (Pxz) -- (P) -- (Pxy) -- (Px) -- (Pxz) -- (Pz) -- (Pyz) -- (P);
%   \draw[thick]
%   (Pyz) -- (Py) -- (Pxy);

%   \node[label=above:$P$,fill,circle,inner sep=1.75pt] at (P) {};
%   \node[label=below left:$Px$,fill,circle,inner sep=1.75pt] at (Px) {};
%   \node[label=below right:$Py$,fill,circle,inner sep=1.75pt] at (Py) {};
%   \node[label=above:$Pz$,fill,circle,inner sep=1.75pt] at (Pz) {};
%   \node[label=below:$Pxy$,fill,circle,inner sep=1.75pt] at (Pxy) {};
%   \node[label=above right:$Pyz$,fill,circle,inner sep=1.75pt] at (Pyz) {};
%   \node[label=above left:$Pxz$,fill,circle,inner sep=1.75pt] at (Pxz) {};
%   \node[label=above right:$O$,fill,circle,inner sep=1.75pt] at (O) {};
% \end{tikzpicture}
\section*{Appendix}
